Ecosystem functional response across precipitation extremes in a sagebrush steppe

### 2017-08-25 manuscript/usses_water_ms.Rmd
fixes typos

First, altered precipitation changes neither ecosystem functional response nor community composition (Fig. 1, top left).
In this case, changes in ANPP simply follow the soil moisture-ANPP relationship under ambient conditions.
This corresponds to the early phases of the Hierarchical Respone Framework, where ecosystem response follows the physiological responses of individual species.
Second, the ecosystem functional response changes but community composition remains the same (Fig. 1, top right).
A saturating soil moisture-ANPP response fits this scenario, where individual species hit physiological thresholds or are limited by some other resource.
Third, the ecosystem functional response is consistent but underlying community composition changes (Fig. 1, bottom left).
In this case, changes in species' identities or abundances occur in response to altered precipitation levels and species more suited to the new conditions compensate for reduced function of initial species.
Fourth, and last, both ecosystem functional response and community composition change (Fig. 1, bottom right).
New species, or newly abundant species, with different physiological responses completely reshape the ecosystem functional response.

@@

\noindent{}where $\Sigma$ is the variance-covariance matrix and *j(i)* reads as "plot *j* associated with observation *i*". 
The random year effects ($\boldsymbol{\eta}$) are drawn from a normal prior with mean 0 and standard deviation $\sigma_{\text{year}}$, which was drawn from a half-cauchy distribution. 
A full description of our model is in Appendix 2.

@@

The results of our five year experiment in a sagebrush steppe conform to two of our four predictions, depending on treatment.
Neither ecosystem functional response nor community composition changed under chronic drought (Fig. 3A, Fig. 4), consistent with the top left prediction in Fig. 1.
Ecosystem functional response under chronic irrigation was different from the control treatment, but community composition remained unchanged (Fig. 3A, Fig. 4), consistent with the top right prediction in Fig. 1.
The altered ecosystem functional response under irrigation matched our expectations becuase we found evidence for a saturating response for the irrigation treatment (Fig. 3A, right panel).
However, the response of ANPP to soil moisture in all treatments was consistently weak (Table 1, Fig. A2-2) and within-year variation of ANPP was large (Fig. 3B)

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=4in]{../figures/hypothesis_figtable.png}
  \caption{Possible outcomes of chronic resource alteration based on the 'Hierachical Response Framework' (Smith et al. 2009).}
\end{figure}

>>>>

First, altered precipitation changes neither ecosystem functional response nor community composition (Fig. 1, top left).
In this case, changes in ANPP simply follow the soil moisture-ANPP relationship under ambient conditions.
This corresponds to the early phases of the Hierarchical Response Framework, where ecosystem response follows the physiological responses of individual species.
Second, the ecosystem functional response changes but community composition remains the same (Fig. 1, top right).
A saturating soil moisture-ANPP response fits this scenario, where individual species hit physiological thresholds or are limited by some other resource.
Third, the ecosystem functional response is consistent but underlying community composition changes (Fig. 1, bottom left).
In this case, changes in species' identities or abundances occur in response to altered precipitation levels and species more suited to the new conditions compensate for reduced function of initial species.
Fourth, and last, both ecosystem functional response and community composition change (Fig. 1, bottom right).
New species, or newly abundant species, with different physiological responses completely reshape the ecosystem functional response.

@@

\noindent{}where $\Sigma$ is the variance-covariance matrix and *j(i)* reads as "plot *j* associated with observation *i*". 
The random year effects ($\boldsymbol{\eta}$) are drawn from a normal prior with mean 0 and standard deviation $\sigma_{\text{year}}$, which was drawn from a half-Cauchy distribution. 
A full description of our model is in Appendix 2.

@@

The results of our five year experiment in a sagebrush steppe conform to two of our four predictions, depending on treatment.
Neither ecosystem functional response nor community composition changed under chronic drought (Fig. 3A, Fig. 4), consistent with the top left prediction in Fig. 1.
Ecosystem functional response under chronic irrigation was different from the control treatment, but community composition remained unchanged (Fig. 3A, Fig. 4), consistent with the top right prediction in Fig. 1.
The altered ecosystem functional response under irrigation matched our expectations because we found evidence for a saturating response for the irrigation treatment (Fig. 3A, right panel).
However, the response of ANPP to soil moisture in all treatments was consistently weak (Table 1, Fig. A2-2) and within-year variation of ANPP was large (Fig. 3B)

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=4in]{../figures/hypothesis_figtable.png}
  \caption{Possible outcomes of chronic resource alteration based on the 'Hierarchical Response Framework' (Smith et al. 2009).}
\end{figure}
